A Large-Scale Study of Polymorphism in R

### 2019-04-06 paper/main.tex

\newcommand{\attr}[2]{\ensuremath{#1_{\mathtt{#2}}}\xspace}
\newcommand{\attrclass}[3]{\ensuremath{#1^{\mathtt{#3}}_{\mathtt{#2}}}\xspace}
\renewcommand{\to}{\ensuremath{\rightarrow}\xspace}
\newcommand{\D}{\ensuremath{\small\vec{\mathtt D}}\xspace} % Double
\newcommand{\I}{\ensuremath{\small\vec{\mathtt I}}\xspace} % Integer
\renewcommand{\C}{\ensuremath{\small\vec{\mathtt C}}\xspace} % Character
\renewcommand{\L}{\ensuremath{\small\vec{\mathtt L}}\xspace} % Logical
\newcommand{\R}{\ensuremath{\small\vec{\mathtt R}}\xspace} % Raw
\newcommand{\X}{\ensuremath{\small\vec{\mathtt X}}\xspace} % Complex
\newcommand{\Y}{\ensuremath{\small\vec{\mathtt Y}}\xspace} % Symbol
\newcommand{\sY}{\ensuremath{\small{\mathtt Y}}\xspace} % Symbol
\newcommand{\sS}{\ensuremath{\small{\mathtt S}}\xspace} % S4
\newcommand{\sF}{\ensuremath{\small{\mathtt F}}\xspace} % Closure
\newcommand{\sE}{\ensuremath{\small{\mathtt E}}\xspace} % Env
\renewcommand{\R}{\ensuremath{\small\vec{\mathtt R}}\xspace} % Raw
\newcommand{\sN}{\ensuremath{\small{\mathtt N}}\xspace}     % Null
%\renewcommand{\l}{\ensuremath{\small L<{\mathtt ?}>}\xspace}     % List
\renewcommand{\l}{\ensuremath{\small\underline{\mathtt ?}}\xspace}     % List
\newcommand{\sD}{\ensuremath{\small{\mathtt D}}\xspace} % Double
\newcommand{\sI}{\ensuremath{\small{\mathtt I}}\xspace} % Integer
\newcommand{\sC}{\ensuremath{\small{\mathtt C}}\xspace} % Character
\newcommand{\sL}{\ensuremath{\small{\mathtt L}}\xspace} % Logical
\newcommand{\sX}{\ensuremath{\small{\mathtt X}}\xspace} % Complex
\newcommand{\sR}{\ensuremath{\small{\mathtt R}}\xspace} % Raw
\newcommand{\ANY}{\ensuremath{\small{\mathtt ?}}\xspace}     % Any
\newcommand{\lT}[1]{\ensuremath{\small\underline{\mathtt #1}}\xspace}     % list<T>
\newcommand{\M}[1]{\ensuremath{\attr{\vec{\tt #1}}{mat}}\xspace}     % matrix
\newcommand{\df}{\ensuremath{\attr{\l}{df}}\xspace}     % data.frame

@@

Figure~\ref{fig:charclos} is a function with character and function
polymorphism.  The caller specifies {\tt fn}, which is either a function
{\it or} the name of a function which will be looked up by string.

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrl}
  \hline
Signature & Count & \% of All Signatures \\ 
  \hline
  \D, \M{D} & 4848 & 0.5\% \\ 
  \l, \lT{D} & 1843 & 0.2\% \\ 
  \sC, \sD & 1590 & 0.2\% \\ 
  \M{D}, \M{I} & 1502 & 0.2\% \\ 
  \l, \lT{list} & 1199 & 0.1\% \\ 
  \df, \M{D} & 1180 & 0.1\% \\ 
  \C, \D & 1019 & 0.1\% \\ 
  \sD, \sF & 1005 & 0.1\% \\ 
  \I, \sD & 997 & 0.1\% \\ 
  \sC, \sF & 991 & 0.1\% \\ 
   \hline
\end{tabular}
\caption{Top polymorphic argument signatures in L1.}
\label{tab:toppolyL1}
\end{table}

@@

	\item \l, \lT{list}: here we have a list of any and a list of lists.
	One explanation for this is that lists of lists sometimes contain NULL as an element, and this would show up with type \l, again as we don't do any subtyping while computing precise list types.
	Another explanation is the way R handles object-orientation, which we discuss shortly in Section~\ref{sec:S3S4R5}.

>>>>

\newcommand{\attr}[2]{\ensuremath{#1_{\mathtt{#2}}}\xspace}
\newcommand{\attrclass}[3]{\ensuremath{#1^{\mathtt{#3}}_{\mathtt{#2}}}\xspace}
\renewcommand{\to}{\ensuremath{\rightarrow}\xspace}
\newcommand{\D}{\ensuremath{\small\vec{\mathtt D}}\xspace} % Double
\newcommand{\I}{\ensuremath{\small\vec{\mathtt I}}\xspace} % Integer
\renewcommand{\C}{\ensuremath{\small\vec{\mathtt C}}\xspace} % Character
\renewcommand{\L}{\ensuremath{\small\vec{\mathtt L}}\xspace} % Logical
\newcommand{\R}{\ensuremath{\small\vec{\mathtt R}}\xspace} % Raw
\newcommand{\X}{\ensuremath{\small\vec{\mathtt X}}\xspace} % Complex
\newcommand{\Y}{\ensuremath{\small\vec{\mathtt Y}}\xspace} % Symbol
\newcommand{\sY}{\ensuremath{\small{\mathtt Y}}\xspace} % Symbol
\newcommand{\sS}{\ensuremath{\small{\mathtt S}}\xspace} % S4
\newcommand{\sF}{\ensuremath{\small{\mathtt F}}\xspace} % Closure
\newcommand{\sE}{\ensuremath{\small{\mathtt E}}\xspace} % Env
\renewcommand{\R}{\ensuremath{\small\vec{\mathtt R}}\xspace} % Raw
\newcommand{\sN}{\ensuremath{\small{\mathtt N}}\xspace}     % Null
%\renewcommand{\l}{\ensuremath{\small L<?>}\xspace}     % List
\renewcommand{\l}{\ensuremath{\small\underline{\mathtt ?}}\xspace}     % List
\newcommand{\sD}{\ensuremath{\small{\mathtt D}}\xspace} % Double
\newcommand{\sI}{\ensuremath{\small{\mathtt I}}\xspace} % Integer
\newcommand{\sC}{\ensuremath{\small{\mathtt C}}\xspace} % Character
\newcommand{\sL}{\ensuremath{\small{\mathtt L}}\xspace} % Logical
\newcommand{\sX}{\ensuremath{\small{\mathtt X}}\xspace} % Complex
\newcommand{\sR}{\ensuremath{\small{\mathtt R}}\xspace} % Raw
\newcommand{\ANY}{\ensuremath{\small{\mathtt ?}}\xspace}     % Any
\newcommand{\lT}[1]{\ensuremath{\small\underline{\mathtt{#1}}}\xspace}     % list<T>
\newcommand{\M}[1]{\ensuremath{\attr{\vec{\tt #1}}{mat}}\xspace}     % matrix
\newcommand{\df}{\ensuremath{\attr{\l}{df}}\xspace}     % data.frame

@@

Figure~\ref{fig:charclos} is a function with character and function
polymorphism.  The caller specifies {\tt fn}, which is either a function
{\it or} the name of a function which will be looked up by name (a string).

@@

\begin{table}[ht]
\centering
\begin{tabular}{lrl}
  \hline
Signature & Count & \% of All Signatures \\ 
  \hline
  \D, \M{D} & 4848 & 0.5\% \\ 
  \l, \lT{D} & 1843 & 0.2\% \\ 
  \sC, \sD & 1590 & 0.2\% \\ 
  \M{D}, \M{I} & 1502 & 0.2\% \\ 
%  \l, \lT{list} & 1199 & 0.1\% \\ 
  \df, \M{D} & 1180 & 0.1\% \\ 
  \C, \D & 1019 & 0.1\% \\ 
  \sD, \sF & 1005 & 0.1\% \\ 
  \I, \sD & 997 & 0.1\% \\ 
  \sC, \sF & 991 & 0.1\% \\ 
   \hline
\end{tabular}
\caption{Top polymorphic argument signatures in L1.}
\label{tab:toppolyL1}
\end{table}

@@

%	\item \l, \lT{list}: here we have a list of any and a list of lists.
%	One explanation for this is that lists of lists sometimes contain NULL as an element, and this would show up with type \l, again as we don't do any subtyping while computing precise list types.
%	Another explanation is the way R handles object-orientation, which we discuss shortly in Section~\ref{sec:S3S4R5}.
